---
title: "plotsStats_2sstim_mixedDiseaseProject"
author: "Kira Shaw"
date: "2024-07-11"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

``` {r, echo = FALSE, message = FALSE}

# load libraries needed for analysis 
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(lmm)
library(lme4)
library(lmerTest)
library(emmeans)
library(psych)

```

```{r, echo  = FALSE}

rm(list = ls(all.names = TRUE))

## 1. READ IN DATA #########################################################################

## load data table: 
data_table <- read_excel("U:\\Kira\\Projects\\Beth_MixedDiseaseModels\\Data\\Exp3_16sStim\\16sStim_data4LMM.xlsx")

## 2. CLEAN DATA TABLE #####################################################################

### create an additional column which groups trials as either early (1-5), late (25-30), or none
data_table$trialGrp <- data_table$trialID
data_table$trialGrp[data_table$trialID<=5]<-'Early'
data_table$trialGrp[data_table$trialID>5 & data_table$trialID<10]<-'Middle'
data_table$trialGrp[data_table$trialID>=10]<-'Late'
# specify this new variable is a factor
data_table <- data_table %>% mutate(trialGrp = factor(trialGrp))

#change sex and grp numbers to words
data_table$sex[data_table$sex==1]<-'Male'
data_table$sex[data_table$sex==2]<-'Female'

data_table$grpID[data_table$grpID==1]<-'AD'
data_table$grpID[data_table$grpID==2]<-'WT'
data_table$grpID[data_table$grpID==3]<-'ATH'
data_table$grpID[data_table$grpID==4]<-'MIX'

## specify which numerical values are factors
data_table <- data_table %>%
  mutate(
    animalID = factor(animalID),
    sessID = factor(sessID),
    expID = factor(expID),
    locoGrp = factor(locoGrp)
    )


```

<font size="10"> Boxplots and LMM results for 16s stim across disease groups: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

## FIGURE 1:

variablesofinterest <- c("hbt_W_maxpk","hbt_W_t2p","hbt_W_AUC","hbt_A_maxpk","hbt_A_t2p","hbt_A_AUC","hbt_V_maxpk","hbt_V_t2p","hbt_V_AUC","hbt_P_maxpk","hbt_P_t2p","hbt_P_AUC")

for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  # stats and plots for vessel ROIs collapsed across experimental groups
  print(variablesofinterest[i]) #display which ts metric
  #Run LMM comparing across vessels, with animal ID as random factor
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = data_table) 
  print(anova(model))
  em_res = emmeans(model, ~ grpID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  #plot as violin 
  p<-ggplot(data_table, aes(x=grpID, y=get(variablesofinterest[i]), fill=grpID)) +
    ylab(variablesofinterest[i])+
  geom_violin(position=position_dodge(1))
  print(p)
    
  ### MALES ONLY TO REMOVE SEX IMPACT
  print(variablesofinterest[i]) #display which ts metric
  #Run LMM comparing across vessels, with animal ID as random factor
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = data_table %>% filter(sex=="Male")) 
  print(anova(model))
  em_res = emmeans(model, ~ grpID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  
} # end of looping ts metrics of interest

# for copying and pasting data into graphpad or excel for plots/data sharing
#t <- data_table %>% filter(vessID=="dv" & grpID==4)
#clipr::write_clip(t$minpk)


# also run stats on loco_auc between groups as need to know whether different experimental groups differences could be driven by significantly different levels of loco 
print("Check for differences in locomotion across exp grps, both sexes")
model <- lmer(loco_AUC~grpID + (1|animalID), data = data_table) 
print(anova(model))
print("Check for differences in locomotion across exp grps, male only")
model <- lmer(loco_AUC~grpID + (1|animalID), data = data_table %>% filter(sex=="Male")) 
print(anova(model))
# NB no sig diffs in loco_auc across grps so dnt need pairwise
#em_res = emmeans(model, ~ grpID)
#print(pairs(em_res))

rm(em_res,model,p,p1,i) #remove unused variables to tidy work space

  
```

<font size="10"> Checking for sex differences: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

## SUPP FIGURE 1:

variablesofinterest <- c("hbt_W_maxpk","hbt_W_t2p","hbt_W_AUC", "hbt_W_reqPk","hbr_W_maxpk","hbr_W_t2p","hbr_W_AUC",
                         "hbt_A_maxpk","hbt_A_t2p","hbt_A_AUC", "hbt_A_reqPk", "hbr_A_maxpk","hbr_A_t2p","hbr_A_AUC",
                         "hbt_V_maxpk","hbt_V_t2p","hbt_V_AUC", "hbt_V_reqPk", "hbr_V_maxpk","hbr_V_t2p","hbr_V_AUC")

for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  
  # stats and plots for vessel ROIs collapsed across experimental groups
  print(variablesofinterest[i]) #display which ts metric
  #Run LMM comparing across vessels, with animal ID as random factor
  model <- lmer(get(variablesofinterest[i])~grpID*sex + (1|animalID), data = data_table %>% filter(grpID=="AD" | grpID=="WT")) 
  print(anova(model))
  #em_res = emmeans(model, ~ grpID) #emmeans() corrects p values for multiple comparisons 
  #print(pairs(em_res)) 
  #plot as violin 
  p<-ggplot(data_table %>% filter(grpID=="AD" | grpID=="WT"), aes(x=sex, y=get(variablesofinterest[i]), fill=sex)) +
    facet_wrap(~ grpID)+
    ylab(variablesofinterest[i])+
  geom_violin(position=position_dodge(1))
  print(p)
  
} # end of looping ts metrics of interest

# for copying and pasting data into graphpad or excel for plots/data sharing
#t <- data_table %>% filter(vessID=="dv" & grpID==4)
#clipr::write_clip(t$minpk)


# also run stats on loco_auc between groups as need to know whether different experimental groups differences could be driven by significantly different levels of loco 
print("Check for differences in locomotion across exp grps")
model <- lmer(loco_AUC~grpID*sex + (1|animalID), data = data_table %>% filter(grpID=="AD" | grpID=="WT")) 
print(anova(model))
# NB no sig diffs in loco_auc across grps so dnt need pairwise
#em_res = emmeans(model, ~ grpID)
#print(pairs(em_res))

rm(em_res,model,p,p1,i) #remove unused variables to tidy work space

  
```

<font size="10"> Exploring impact of locomotion on haem responses: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

## FIGURE 2:

# correlation plots looking at loco AUC by hbt AUC separated across ROI categories and by disease

variablesofinterest <- c("hbt_W_AUC","hbt_A_AUC","hbt_V_AUC","hbt_P_AUC")

for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  # see if locomotion AUC correlates with min peak or max peak values
  p2 <- ggplot(data_table, aes(x=loco_AUC, y=get(variablesofinterest[i]),color=grpID)) +
    geom_point(size=1) +
    ggtitle('Correlating locomotion with haem responses') +
    geom_smooth(method=lm, se=FALSE, fullrange=FALSE)+ 
    #facet_wrap(~ grpID)+
    ylab(variablesofinterest[i])+
    theme_classic(base_size = 14)
    #theme(legend.position = "none")
  print(p2)
  
  #STATS: CORR
  print(variablesofinterest[i])
  
  #t <- data_table %>% filter(vessID=="dv")
  ##clipr::write_clip(t$loco_auc)
  #clipr::write_clip(t$minpk)
  
  print("Group 1:")
  t <- data_table %>% filter(grpID=="AD")
  print(cor.test(formula = ~loco_AUC+get(variablesofinterest[i]), data=t))
  
  print("Group 2:")
  t <- data_table %>% filter(grpID=="WT")
  print(cor.test(formula = ~loco_AUC+get(variablesofinterest[i]), data=t))
  
  print("Group 3:")
  t <- data_table %>% filter(grpID=="ATH")
  print(cor.test(formula = ~loco_AUC+get(variablesofinterest[i]), data=t))
  
  print("Group 4:")
  t <- data_table %>% filter(grpID=="MIX")
  print(cor.test(formula = ~loco_AUC+get(variablesofinterest[i]), data=t))

  
} # end of looping ts metrics of interest


  
```

<font size="10"> Boxplots and LMM results for 16s stim across disease groups AND locomotion condition: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

## FIGURE 3:

variablesofinterest <- c("hbt_W_maxpk","hbt_W_t2p","hbt_W_t2o","hbt_W_AUC","hbt_A_maxpk","hbt_A_t2p","hbt_A_t2o","hbt_A_AUC","hbt_V_maxpk","hbt_V_t2p","hbt_V_t2o","hbt_V_AUC","hbt_P_maxpk","hbt_P_t2p","hbt_P_t2o","hbt_P_AUC")

for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  # stats and plots for vessel ROIs collapsed across experimental groups
  print(variablesofinterest[i]) #display which ts metric
  #Run LMM comparing across vessels, with animal ID as random factor
  model <- lmer(get(variablesofinterest[i])~grpID*locoGrp + (1|animalID), data = data_table) 
  print(anova(model))
 # em_res = emmeans(model, ~ grpID*locoGrp) #emmeans() corrects p values for multiple comparisons 
 # print(pairs(em_res)) 
  
  ## Due to there being SO many multiple comparisons, to explore the differences further, stats were run within loco condition to compare between grps
  print('Grp 1')
  t <- data_table %>% filter(locoGrp=="1")
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = t) 
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  
  print('Grp 2')
  t <- data_table %>% filter(locoGrp=="2")
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = t) 
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  
  print('Grp 3')
  t <- data_table %>% filter(locoGrp=="3")
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = t) 
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  
  print('Grp 4')
  t <- data_table %>% filter(locoGrp=="4")
  model <- lmer(get(variablesofinterest[i])~grpID + (1|animalID), data = t) 
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  
  #plot as violin 
  p<-ggplot(data_table, aes(x=grpID, y=get(variablesofinterest[i]), fill=grpID)) +
    ylab(variablesofinterest[i])+
  geom_violin(position=position_dodge(1))+
  facet_wrap(~locoGrp)  
  print(p)
  
} # end of looping ts metrics of interest

# for copying and pasting data into graphpad or excel for plots/data sharing
#t <- data_table %>% filter(vessID=="dv" & grpID==4)
#clipr::write_clip(t$minpk)



  
```

<font size="10"> Impact of trial number (1-15) or experimental day (1-2) - scatterplots: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

## FIGURE 4

## scatterplots and correlations to look at loco AUC and hbt AUC against trial number 
variablesofinterest <- c("loco_AUC","hbt_W_AUC","hbt_A_AUC","hbt_V_AUC","hbt_P_AUC")

data_table <- data_table %>% filter(expID!="3")

for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  
  # see if locomotion AUC correlates with min peak or max peak values
  p1 <- ggplot(data_table, aes(x=trialID, y=get(variablesofinterest[i]))) +
    geom_point(size=1) +
    ggtitle('Impact of trial number') +
    geom_smooth(method=lm, se=FALSE, fullrange=FALSE)+ 
    #facet_wrap(~ grpID)+
    ylab(variablesofinterest[i])+
    theme_classic(base_size = 14)
    #theme(legend.position = "none")
  print(p1)
  
    #STATS: CORR
  print(variablesofinterest[i])
  print("Collapsed across all groups")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=data_table))
  
  # see if locomotion AUC correlates with min peak or max peak values
  p2 <- ggplot(data_table, aes(x=trialID, y=get(variablesofinterest[i]),color=grpID)) +
    geom_point(size=1) +
    ggtitle('Impact of trial number') +
    geom_smooth(method=lm, se=FALSE, fullrange=FALSE)+ 
    facet_wrap(~expID)+
    ylab(variablesofinterest[i])+
    theme_classic(base_size = 14)
    #theme(legend.position = "none")
  print(p2)
  
  #STATS: CORR
  print(variablesofinterest[i])
  
  print("Group 1, Imaging Day 1:")
  t <- data_table %>% filter(grpID=="AD" & expID=="1")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  print("Group 1, Imaging Day 2:")
  t <- data_table %>% filter(grpID=="AD" & expID=="2")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  
  
  print("Group 2, Imaging Day 1:")
  t <- data_table %>% filter(grpID=="WT" & expID=="1")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  print("Group 2, Imaging Day 2:")
  t <- data_table %>% filter(grpID=="WT" & expID=="2")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  
  print("Group 3, Imaging Day 1:")
  t <- data_table %>% filter(grpID=="ATH" & expID=="1")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  print("Group 3, Imaging Day 2:")
  t <- data_table %>% filter(grpID=="ATH" & expID=="2")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  
  print("Group 4, Imaging Day 1:")
  t <- data_table %>% filter(grpID=="MIX" & expID=="1")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))
  print("Group 4, Imaging Day 2:")
  t <- data_table %>% filter(grpID=="MIX" & expID=="2")
  print(cor.test(formula = ~trialID+get(variablesofinterest[i]), data=t))

  
} # end of looping ts metrics of interest

```

<font size="10"> Impact of trial number (1-15) - boxplots and LMMs: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

variablesofinterest <- c("hbt_W_maxpk","hbt_W_t2p","hbt_W_t2o","hbt_W_AUC","hbt_A_maxpk","hbt_A_t2p","hbt_A_t2o","hbt_A_AUC","hbt_V_maxpk","hbt_V_t2p","hbt_V_t2o","hbt_V_AUC","hbt_P_maxpk","hbt_P_t2p","hbt_P_t2o","hbt_P_AUC")

## FIGURE 4

###### impact of trial number

# general impact of trial number or exp day on metrics
  print("Check for differences of exp day or trial ID on loco AUC")
  model <- lmer(loco_AUC~trialGrp + (1|animalID), data = t) 
  print(anova(model))


t <- data_table %>% filter(trialGrp!="Middle") #remove 'middle' trials and only look at early or late trials

## COLLAPSE ACROSS DISEASE GRPS
# run LMM to compare early to late trials per loco cond, and plot metrics
for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  # stats and plots for vessel ROIs collapsed across experimental groups
  print(variablesofinterest[i]) #display which ts metric
  
    #individual datapts, colour coded by animal ID, facet wrap to visualise per grp
  p1 <- t %>%
  ggplot(aes(x=trialGrp, y=get(variablesofinterest[i]), fill=trialGrp)) +
    geom_violin(position=position_dodge(1)) +
  ylab(variablesofinterest[i]) +
  xlab('Trial Grp')+
  theme_classic(base_size = 14)+
  theme(legend.position = "right")+ #"right"
  facet_wrap(~locoGrp)
  print(p1)
  
  # general impact of trial number or exp day on metrics
  print("Check for differences of exp day or trial ID on haem AUC")
  model <- lmer(get(variablesofinterest[i])~trialGrp + (1|animalID), data = t) 
  print(anova(model))
  
  model <- lmer(get(variablesofinterest[i])~trialGrp*locoGrp + (1|animalID), data = t) 
  print(anova(model))
  #em_res = emmeans(model, ~ trialGrp*locoGrp) #emmeans() corrects p values for multiple comparisons 
  #print(pairs(em_res)) 
  
  ## Due to there being SO many multiple comparisons, to explore the differences further, stats were run within loco condition to compare between grps
  print('Loco Grp 1')
  model <- lmer(get(variablesofinterest[i])~trialGrp + (1|animalID), data = t%>% filter(locoGrp=="1")) 
  print(anova(model))
  em_res = emmeans(model, ~ trialGrp) 
  print(pairs(em_res))
  
  print('Loco Grp 2')
  model <- lmer(get(variablesofinterest[i])~trialGrp + (1|animalID), data = t%>% filter(locoGrp=="2")) 
  em_res = emmeans(model, ~ trialGrp) 
  print(pairs(em_res))

  
  print('Loco Grp 3')
  model <- lmer(get(variablesofinterest[i])~trialGrp + (1|animalID), data = t%>% filter(locoGrp=="3")) 
  em_res = emmeans(model, ~ trialGrp) 
  print(pairs(em_res))

  print('Loco Grp 4')
  model <- lmer(get(variablesofinterest[i])~trialGrp + (1|animalID), data = t%>% filter(locoGrp=="4")) 
  em_res = emmeans(model, ~ trialGrp) 
  print(pairs(em_res))

  
  p1 <- t %>%
  ggplot(aes(x=trialGrp, y=get(variablesofinterest[i]), fill=grpID)) +
    geom_violin(position=position_dodge(1)) +
  ylab(variablesofinterest[i]) +
  xlab('Trial Grp')+
  theme_classic(base_size = 14)+
  theme(legend.position = "none")+ #"right"
  facet_wrap(~locoGrp)
  print(p1)
  
  print('Loco Grp 1')
  model <- lmer(get(variablesofinterest[i])~trialGrp*grpID + (1|animalID), data = t%>% filter(locoGrp=="1")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ trialGrp*grpID) 
  print(pairs(em_res))

  print('Loco Grp 2')
  model <- lmer(get(variablesofinterest[i])~trialGrp*grpID + (1|animalID), data = t%>% filter(locoGrp=="2")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ trialGrp*grpID) 
  print(pairs(em_res))
    
  print('Loco Grp 3')
  model <- lmer(get(variablesofinterest[i])~trialGrp*grpID + (1|animalID), data = t%>% filter(locoGrp=="3")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ trialGrp*grpID) 
  print(pairs(em_res))
  
  print('Loco Grp 4')
  model <- lmer(get(variablesofinterest[i])~trialGrp*grpID + (1|animalID), data = t%>% filter(locoGrp=="4")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ trialGrp*grpID) 
  print(pairs(em_res))
  
  
} # end of looping ts metrics of interest


```

<font size="10"> Impact of experimental day (1-2)- boxplots and LMMs: </font> 

```{r, fig.height=10, fig.width=10, echo = FALSE, message=FALSE}

variablesofinterest <- c("hbt_W_maxpk","hbt_W_t2p","hbt_W_t2o","hbt_W_AUC","hbt_A_maxpk","hbt_A_t2p","hbt_A_t2o","hbt_A_AUC","hbt_V_maxpk","hbt_V_t2p","hbt_V_t2o","hbt_V_AUC","hbt_P_maxpk","hbt_P_t2p","hbt_P_t2o","hbt_P_AUC")

## FIGURE 5

  ## impact of exp day #########################################################

  print('Impact of exp day on loco auc across all loco conditions')
  model <- lmer(loco_AUC~expID + (1|animalID), data = data_table) 
  print(anova(model))
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  
  # check for running differences across experimental days within loco grps
  print('Loco Grp 1')
  t <- data_table %>% filter(locoGrp=="1")
  model <- lmer(loco_AUC~expID + (1|animalID), data = t) 
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  print('Loco Grp 2')
  t <- data_table %>% filter(locoGrp=="2")
  model <- lmer(loco_AUC~expID + (1|animalID), data = t) 
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  print('Loco Grp 3')
  t <- data_table %>% filter(locoGrp=="3")
  model <- lmer(loco_AUC~expID + (1|animalID), data = t) 
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 
  print('Loco Grp 4')
  t <- data_table %>% filter(locoGrp=="4")
  model <- lmer(loco_AUC~expID + (1|animalID), data = t) 
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 

# run LMM to compare exp day 1 to exp day 4 and separate by loco cond
# WARNING- for loco cond 3 and 4, still running more on day 1 so not too useful 
for(i in 1:length(variablesofinterest)) { #loop ts metrics of interest
  
  # stats and plots for vessel ROIs collapsed across experimental groups
  print(variablesofinterest[i]) #display which ts metric
  
  # general impact of  exp day on metrics
  print("Check for differences of exp day or trial ID on haem AUC")
  model <- lmer(get(variablesofinterest[i])~expID + (1|animalID), data = data_table) 
  print(anova(model))
  em_res = emmeans(model, ~expID) #emmeans() corrects p values for multiple comparisons 
  print(pairs(em_res)) 

  #individual datapts, colour coded by animal ID, facet wrap to visualise per grp
  p1 <- data_table %>%
  ggplot(aes(x=expID, y=get(variablesofinterest[i]), fill=expID)) +
    geom_violin(position=position_dodge(1)) +
  ylab(variablesofinterest[i]) +
  xlab('ExpDay')+
  theme_classic(base_size = 14)+
  theme(legend.position = "right")+ #"right"
  facet_wrap(~locoGrp)
  print(p1)
  
  model <- lmer(get(variablesofinterest[i])~expID*locoGrp + (1|animalID), data = data_table) 
  print(anova(model))
  
  ## Due to there being SO many multiple comparisons, to explore the differences further, stats were run within loco condition to compare between grps
  print('Loco Grp 1')
  model <- lmer(get(variablesofinterest[i])~expID + (1|animalID), data = data_table%>% filter(locoGrp=="1")) 
  em_res = emmeans(model, ~ expID) 
  print(pairs(em_res))

  print('Loco Grp 2')
  model <- lmer(get(variablesofinterest[i])~expID + (1|animalID), data = data_table%>% filter(locoGrp=="2")) 
  em_res = emmeans(model, ~ expID) 
  print(pairs(em_res))

  print('Loco Grp 3')
  model <- lmer(get(variablesofinterest[i])~expID + (1|animalID), data = data_table%>% filter(locoGrp=="3")) 
  em_res = emmeans(model, ~ expID) 
  print(pairs(em_res))

  print('Loco Grp 4')
  model <- lmer(get(variablesofinterest[i])~expID + (1|animalID), data = data_table%>% filter(locoGrp=="4")) 
  em_res = emmeans(model, ~ expID) 
  print(pairs(em_res))

  
p1 <- data_table %>%
  ggplot(aes(x=expID, y=get(variablesofinterest[i]), fill=grpID)) +
    geom_violin(position=position_dodge(1)) +
  ylab(variablesofinterest[i]) +
  xlab('ExpDay')+
  theme_classic(base_size = 14)+
  theme(legend.position = "right")+ #"right"
  facet_wrap(~locoGrp)
  print(p1)
  
  print('Loco Grp 1')
  model <- lmer(get(variablesofinterest[i])~expID*grpID + (1|animalID), data = data_table%>% filter(locoGrp=="1")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ expID*grpID) 
  print(pairs(em_res))
  
  print('Loco Grp 2')  
  model <- lmer(get(variablesofinterest[i])~expID*grpID + (1|animalID), data = data_table%>% filter(locoGrp=="2")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ expID*grpID) 
  print(pairs(em_res))
  
  print('Loco Grp 3')  
  model <- lmer(get(variablesofinterest[i])~expID*grpID + (1|animalID), data = data_table%>% filter(locoGrp=="3")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ expID*grpID) 
  print(pairs(em_res))
  
  print('Loco Grp 4')  
  model <- lmer(get(variablesofinterest[i])~expID*grpID + (1|animalID), data = data_table%>% filter(locoGrp=="4")) 
  print(anova(model))
  print('disease only compare')
  em_res = emmeans(model, ~ grpID) 
  print(pairs(em_res))
  print('disease AND exp day compare')
  em_res = emmeans(model, ~ expID*grpID) 
  print(pairs(em_res))
  
  
} # end of looping ts metrics of interest

# for copying and pasting data into graphpad or excel for plots/data sharing
#t <- data_table %>% filter(vessID=="dv" & grpID==4)
#clipr::write_clip(t$minpk)


```
